\vspace{-2cm} Government Websites As Data: \\ A methodological pipeline with application to the websites of municipalities in the United States

### 2021-09-24 paper/jitp_rr_memo/jitp_rr2_memo.tex
addressed reviewer points

Thank you for your comments and for giving us the opportunity to revise and resubmit our paper. Thanks also to Reviewer 1 for their constructive comments. As we hope you will see both in the revised manuscript and in this response letter, we have taken each comment seriously and have endeavored to address each as completely as possible. Each of the comments s addressed in the order presented in the review.  We should note that we are now approximately NNN words over the 5,000 word limit. We trimmed the text substantially as we revised the paper, but we think the current version provides the most effective presentation of our core contributions and the revisions suggested by the reviewers. Of course, we are happy to trim further if necessary.  We do believe that addressing reviewers' comments has significantly improved the paper. \\

@@

	\textbf{Response}:

@@

	\textbf{Response}:

>>>>

Thank you for your comments and for giving us the opportunity to revise and resubmit our paper. Thanks also to Reviewer 1 for their constructive comments. As we hope you will see both in the revised manuscript and in this response letter, we have taken each comment seriously and have endeavored to address each as completely as possible. Each of the comments s addressed in the order presented in the review.  We should note that we are now approximately 500 words over the 5,000 word limit. We trimmed the text substantially as we revised the paper, but we think the current version provides the most effective presentation of our core contributions and the revisions suggested by the reviewers. Of course, we are happy to trim further if necessary.  We do believe that addressing reviewers' comments has significantly improved the paper. \\

@@

	\textbf{Response}:  We revised this section to note the connection/relevance. We note that it is now standard practice for researchers to conduct ``supervised'' or ``human-in-the-loop'' machine coding exercises in which a relatively small number of human-coded items are used to train a machine classification algorithm such that a large set of items can be machine-coded. Given the ubiquity and effectiveness of human-coding attributes of government websites, there is substantial potential for supervised machine coding. However, in order to train a machine classifier, researchers must have access to website contents in a machine-readable format. Our pipeline can be used to collect such website content from a large set of websites.

@@

	\textbf{Response}:  We removed the discussion of these studies from the conclusion. We added a brief paragraph to Section 2, in which we discuss the fact that researchers in other areas---beyond the analysis of government websites---have conducted computational content analyses of websites. We point to these studies as evidence that our pipeline will be applicable beyond the study of government websites.

### 2021-09-24 paper/manuscript_jitp_rr2.tex
started revisions for R&R 2 at JITP
addressed reviewer points

%==============Packages & Commands==============
\usepackage{graphicx}
\usepackage{fancyvrb}
\usepackage{tikz}
%%%<
\usepackage{verbatim}
%\usepackage[active,tightpage]{preview}
%\PreviewEnvironment{tikzpicture} 
%\setlength\PreviewBorder{5pt}%

@@

The content of a government's website is an important source of information about policy priorities,  procedures, and services. Existing research on government websites has relied on manual methods of website content collection and processing, which imposes cost limitations on the scale of website data collection. In this research note, we propose that the automated collection of website content from large samples of government websites can offer relief from the costs of manual collection, and enable contributions through large-scale comparative analyses.  We also provide software to ease the use of this data collection method. In an illustrative application, we collect textual content from the websites of over two hundred municipal governments in the United States, and study how website content is associated with mayoral partisanship. Using statistical topic modeling, we find that the partisanship of the mayor predicts differences in the contents of city websites that align with differences in the platforms of Democrats and Republicans. The application validates the utility of website content data extracted via our methodological pipeline.

@@

The manual approach is expensive, and is also subject to human error, judgement calls, and inter-coder reliability problems. Furthermore, researchers looking only for specific pieces of information are bound to miss a lot of content that doesn't fall within their pre-defined objectives. Moreover, city websites often contain thousands of pages \citep{Urban2002}\footnote{\cite{Urban2002} relies on a webcrawler to measure how many pages each city website is comprised of, which is also the first step of \texttt{wget}. In this way, his research is a precursor to our own, albeit without the actual analysis of each page.}, so even projects with substantial human resources might struggle to provide a complete understanding of individual websites. Conversely, scrapers conventionally used in the social sciences (see, for example, \citealt{cryer2019navigating}) rely on extracting text through specific HTML tags, which makes it difficult to apply to a large number of websites, because the process needs to be adjusted for each one. By contrast, the only input our pipeline requires is the URL, and the only limits are bandwidth, processing power and storage space.

@@

We have highlighted projects focused on government and politician websites. However, the application of the methods we propose is not limited to government and politician websites. Our pipeline can be used in the context of any project that would benefit from the analysis of textual content from a large population of websites. For example, \citet{coyle2020no} analyze the content of company websites to find manufacturing companies that use contract manufacturing arrangements in their business models. \citet{kluver2015measuring} use the textual content presented on interest group websites to classify the groups' issue agendas and constituencies. There is a broad body of research programs that could make use of the data collection and processing pipeline we present.

>>>>

%==============Packages & Commands==============
\usepackage{graphicx}
\usepackage{color,soul}
\usepackage{tikz}
%%%<
\usepackage{verbatim}
%\usepackage[active,tightpage]{preview}
%\PreviewEnvironment{tikzpicture} 
%\setlength\PreviewBorder{5pt}%

@@

The content of a government's website is an important source of information about policy priorities,  procedures, and services. Existing research on government websites has relied on manual methods of website content collection and processing, which imposes cost limitations on the scale of website data collection. In this research note, we propose that the automated collection of website content from large samples of government websites can offer relief from the costs of manual collection, and enable contributions through large-scale comparative analyses.  We also provide software to ease the use of this data collection method. In an illustrative application, we collect textual content from the websites of over two hundred municipal governments in the United States, and study how website content is associated with mayoral partisanship. Using statistical topic modeling, we find that the partisanship of the mayor predicts differences in the contents of city websites that align with differences in the platforms of Democrats and Republicans. The application \hl{illustrates} the utility of website content data extracted via our methodological pipeline.

@@

The manual approach is expensive, and is also subject to human error, judgement calls, and inter-coder reliability problems. Furthermore, researchers looking only for specific pieces of information are bound to miss a lot of content that doesn't fall within their pre-defined objectives. Moreover, city websites often contain thousands of pages \citep{Urban2002}\footnote{\cite{Urban2002} relies on a webcrawler to measure how many pages each city website is comprised of, which is also the first step of \texttt{wget}. In this way, his research is a precursor to our own, albeit without the actual analysis of each page.}, so even projects with substantial human resources might struggle to provide a complete understanding of individual websites. \hl{It is now standard practice to combine human coding with machine-learning based content classification} \citep[e.g., ][]{sebHok2021multiclass,fowler2021political}. \hl{If researchers had access to machine-readable content associated with government websites, a smaller quantity of human coding could be used to develop machine classifiers for attributes of interest, which could in tern be used to classify much larger sets of websites than is possible to do with human-only coding methods.} Unfortunately, scrapers conventionally used in the social sciences \citep[e.g.,][]{cryer2019navigating} rely on extracting text through specific HTML tags, which makes it difficult to apply to a large number of websites, because the process needs to be adjusted for each site. By contrast, the only input our pipeline requires is the site URL.

\hl{Though our main focus in the current article is on the application to government websites, it is important to note that the pipeline we develop will be useful in the context of many other research designs that involve the collection of website content. Though we are not familiar with existing applications of automated text analysis to government websites, previous work in other domains has involved computational content analysis of websites.} \hl{For example, }\citet{coyle2020no} \hl{analyze the content of company websites to find manufacturing companies that use contract manufacturing arrangements in their business models.} \citet{kluver2015measuring} \hl{use the textual content presented on interest group websites to classify the groups' issue agendas and constituencies.}

@@

We have highlighted projects focused on government and politician websites. However, the application of the methods we propose is not limited to government and politician websites. Our pipeline can be used in the context of any project that would benefit from the analysis of textual content from a large population of websites. There is a broad body of research programs that could make use of the data collection and processing pipeline we present.
